Data for ms. 1

### 2017-05-12 ms1/ms1.Rmd
table of cc prevalence

@@

@@

  list(totals=totals,
       claims_by_class=claims_by_class,
       top_abx=top_abx,
       claims_by_sex=claims_by_sex,
       claims_by_race=claims_by_race,
       claims_by_age=claims_by_age,
       chars_by_age_group=chars_by_age_group,
       claims_by_region=claims_by_region,
       chars_by_consumption=chars_by_consumption,
       condition_model=condition_model,
       big_model=big_model) %>%
    lapply(function(x) mutate(x, year=year))
}

@@

@@

>>>>

# To do

- Remove visits from the models, since we expect that visits are casually in between disease and antibiotics
- Put all years together, put calendar year into the model, and regress (rather than doing separate regressions on each year)

@@

  condition_prevalence = dat$bene %>%
    select(AMI:HYPOTH) %>%
    summarize_all(mean) %>%
    gather('condition', 'prevalence', everything())

@@

  list(totals=totals,
       claims_by_class=claims_by_class,
       top_abx=top_abx,
       claims_by_sex=claims_by_sex,
       claims_by_race=claims_by_race,
       claims_by_age=claims_by_age,
       chars_by_age_group=chars_by_age_group,
       claims_by_region=claims_by_region,
       chars_by_consumption=chars_by_consumption,
       condition_prevalence=condition_prevalence,
       condition_model=condition_model,
       big_model=big_model) %>%
    lapply(function(x) mutate(x, year=year))
}

@@

```{r arrange_condition_prevalence}
condition_prevalence = data_by_field('condition_prevalence') %>%
  spread(year, prevalence) %>%
  arrange(desc(`2011`)) %>%
  kable
```

@@

# Prevalence of conditions

`r condition_prevalence`
